Multisensor Architecture for an Intersection Management System

### 2018-06-18 ch3-arch_sys.tex
General drafting fixes.

\todo{Simulators description (?)}

@@

As mentioned in section \ref{s23}, POSS-i and Ko-PER projects are leading the development of multisensor Intersection Management Systems. One of the contributions of these projects is the creation of datasets of such systems. They provide camera and laser information of a monitored intersection in Peking, China and Aschaffenburg, Germany, respectively. Next, a description of these two datasets will be given.

\subsubsection{POSSi Dataset } \label{possi_ds}

POSSi dataset\footnote{Available at http://www.poss.pku.edu.cn/download.html}

\todo{Dataset description (?)}

\subsubsection{KoPER Dataset }

Ko-PER dataset\footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html}

The full description of this dataset is presented in \cite{Strigel2014}.

>>>>

%\todo{Simulators description (?)}

@@

As mentioned in section \ref{s23}, POSS-i \footnote{Available at http://www.poss.pku.edu.cn/download.html} and Ko-PER \footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html} projects are leading the development of multisensor Intersection Management Systems. One of the contributions of these projects is the creation of datasets of such systems. They provide camera and laser information of a monitored intersection in Peking, China and Aschaffenburg, Germany, respectively.

%Next, a description of these two datasets will be given.
%
%\subsubsection{POSSi Dataset } \label{possi_ds}
%
%POSSi dataset\footnote{Available at http://www.poss.pku.edu.cn/download.html}
%
%\todo{Dataset description (?)}
%
%\subsubsection{KoPER Dataset }
%
%Ko-PER dataset\footnote{Available at http://www.uni-ulm.de/in/mrm/forschung/datensaetze.html}
%
%The full description of this dataset is presented in \cite{Strigel2014}.

### 2018-06-18 ch5-conclusions.tex
General drafting fixes.

When deploying a system for intersection monitoring, it is desirable to have variety of sensors, because this allows to have more complementary information in order to generate an accurate representation of the interection. But more important than the quantity of sensors, is how the data for all installed sensors will be merged.

@@

Before deploy an interesection management system in a real scenario, validation is a must. Datasets are the best option for doing it, because simulators are still in an early stage. The most suitable simulators, although not conceived for this purpose, are the ones used for autonomous driving platforms. These simulators could allow to include complex sensors like lidars and cameras on infrastructure, and include vehicles with autonomous behaviour in the scenario.

@@

The main contribution derived from the execution of this project is a scalable, modular system for traffic monitoring at an intersection. This system was concieved for use both in experimentation cases and real deployment. The software implementation of the system uses at its core a set of tools and libraries ready for industrial and commercial cases.

@@

In addition to this, a set of software repositories are available, one for the application and another one summarizing available datasets containing intersection data. The purpose of this is to let other people review, test and give their opinion about the system. This feedback would be used for new features and improvements.

@@

Generation of our own dataset. Taking into account that PSI reserch group have a laser-scanner, it would be great to generate a dataset for local intersections. From a low-traffic intersection in the campus to a high-traffic intersection in the surroundings. Allowing to test the system under different conditions and do not depend on 3rd party data.

@@

Integration with other technologies and new trends. At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefullness and relevance of these projects in real deployements. It is important new versions of the system, will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.

>>>>

When deploying a system for intersection monitoring, it is desirable to have variety of sensors, because this allows to have more complementary information in order to generate an accurate representation of the intersection. But more important than the quantity of sensors, is how the data for all installed sensors will be processed and unified.

@@

Before deploying an interesection management system in a real scenario, validation is a must. Datasets are the best option for doing it, because simulators are still in an early stage. The most suitable simulators, although not conceived for this purpose, are the ones used for autonomous driving platforms. These simulators could allow to include complex sensors like lidars and cameras on infrastructure, and include vehicles with autonomous behaviour in the scenario.

@@

The main contribution derived from the execution of this project is a scalable, modular system for traffic monitoring at an intersection. This system was concieved for usage both in experimentation cases and real deployments. The software implementation of the system uses at its core a set of tools and libraries ready for industrial and commercial cases.

@@

In addition to this, a set of software repositories are available, one for the application and another one summarizing available datasets containing intersection data. The purpose of this is to let community review, test and give their opinion about the system. This feedback would be used for new features and improvements.

@@

Generation of our own dataset. Taking into account that PSI research group owns a laser-scanner, it would be great to generate a dataset for local intersections. It could be from a low-traffic intersection in the campus or from a high-traffic intersection in the surroundings. This would allow to test the system under different conditions and do not depend on 3rd party data.

@@

Integration with other technologies and new trends. At this moment, there are many advances and trends that could be used along an intersection management system to improve the usefulness and relevance of these projects in real deployements. It is important that new versions of the system will be aligned with topics like Smart cities for authorities/Government integration, Internet of things as a new massive source of information, Cloud/Fog computing for scalable and distributed processing, or Big Data and Data Analytics for traffic insights and forecasting.
